Isostatic constraint for 2D non-linear gravity inversion on rifted margins

### 2019-10-03 manuscript/manuscript.tex
submitted version after R3 and editor's review

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_X_1_2_1_2-2pts}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. 
	Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$ and $\tilde{\mu}_{2} = 10^{2}$.
	(Bottom panel) True and estimated surfaces,
	initial basement and Moho (initial guess) and a 
	priori information at points on basement and Moho (known depths).
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Gravity disturbance produced by the true 
	model (simulated data), estimated model (predicted data) and 
	by the initial guess (initial guess data). 
	The density contrasts are those shown in 
	Table~\ref{tab:volcanic-margin-model} and $S_{0} = 48$ km.}
	\label{fig:synt-margin-step1}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-2pts}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{3}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step2}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_1-2pts}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 1$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm1}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_11-2pts}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 11$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm11}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_18-2pts}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 18$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm18}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_X_1_2_1_2}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
	Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$, $\tilde{\mu}_{2} = 10^{2}$,
	$\tilde{\mu}_{3} = 10^{1}$ and $\tilde{\mu}_{4} = 10^{2}$.
	(Bottom panel) True and estimated surfaces,
	initial basement and Moho (initial guess) and a 
	priori information at points on basement and Moho (known depths).
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Gravity disturbance produced by the true 
	model (simulated data), estimated model (predicted data) and 
	by the initial guess (initial guess data). 
	The density contrasts are those shown in 
	Table~\ref{tab:simple-model} and $S_{0} = 40$ km.}
	\label{fig:simple-model-step1}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_2_1_2_1_2}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
	Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{2}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:simple-model-step1}.}
	\label{fig:simple-model-step2-u0-2}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
		Estimated model $\mathbf{p}^{(2)}$ 
		obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
		using $\tilde{\mu}_{0} = 10^{3}$.
		The remaining information is the same shown in the caption of
		Figure~\ref{fig:simple-model-step1}.}
	\label{fig:simple-model-step2-u0-3}
}

@@

\plot{map-line-localization}{width=0.8\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Gravity disturbance
	provided by the global gravity field model EIGEN-6C4 \citep{forste2014} at
	the study area. The black straight line indicates the gravity profile over the Pelotas
	basin. The end points of the profile have coordinates (geodetic latitude and longitude) 
	$(-27.72^{\circ}, -48.23^{\circ})$ and $(-29.66^{\circ}, -44.94^{\circ})$. 
	The coordinates are referred to the WGS84 datum.}
	\label{fig:pelotas-location}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_X_1_2_1_2}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$, $\tilde{\mu}_{2} = 10^{2}$,
	$\tilde{\mu}_{3} = 10^{1}$ and $\tilde{\mu}_{4} = 10^{2}$.
	(Bottom panel) Estimated surfaces, initial basement and Moho (initial guess) 
	and a priori information at basement and Moho (known depths).
	The continuous black lines represent a previous interpretation presented 
	by \citet{zalan2015}.
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Observed gravity disturbance, data produced by the estimated
	model (predicted data) and data produced the by the initial approximation (initial guess data).
	We used $S_{0} = 41$ km, density contrasts equal to those shown in Table~\ref{tab:pelotas-model}
	and initial approximation for $\Delta S$ equal to $1$ km.}
	\label{fig:pelotas-step1}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{2}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step2}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_7}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 7$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm7}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_17dot6}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 17.6$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm17dot6}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_19}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 19$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm19}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_17-T07}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Alternative estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}). 
	The differences between this model and those shown in Figures \ref{fig:pelotas-step3-sgm7},
	\ref{fig:pelotas-step3-sgm17dot6} and \ref{fig:pelotas-step3-sgm19} are the
	densities $\rho^{(1)}$ and $\rho^{(2)}$ attributed to the sediments
	and SDR (Table~\ref{tab:pelotas-model}), as well as the parameter 
	$\sigma$ (equation~\ref{eq:elements-wii}).
	In this alternative model, $\rho^{(1)} = 2425$ kg/m$^{3}$,
	$\rho^{(2)} = 2835$ kg/m$^{3}$ and $\sigma = 17$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-alternative}
}

@@

The authors are grateful to the editor designate J. Shragge,
assistant editor E. Gasperikova, associate editor X. Li, reviewers 
J. G. Abdeslem, Bob Ferderer and anonymous reviewers for their questions and suggestions. 
We appreciate having the open-source Python toolkit for geophysical modeling and inversion 
called Fatiando a Terra (Portuguese for “slicing the earth”). V. C. Oliveira Jr was supported 
by fellowships from the brazilian research agencies CNPq (grant no. 308945/2017-4) and 
FAPERJ (grant no. E-26/202.729/2018).

>>>>

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_X_1_2_1_2-2pts-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. 
	Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$ and $\tilde{\mu}_{2} = 10^{2}$.
	(Bottom panel) True and estimated surfaces,
	initial basement and Moho (initial guess) and a 
	priori information at points on basement and Moho (known depths).
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Gravity disturbance produced by the true 
	model (simulated data), estimated model (predicted data) and 
	by the initial guess (initial guess data). 
	The density contrasts are those shown in 
	Table~\ref{tab:volcanic-margin-model} and $S_{0} = 48$ km.}
	\label{fig:synt-margin-step1}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-2pts-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{3}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step2}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_1-2pts-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 1$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm1}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_11-2pts-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 11$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm11}
}

\plot{B-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-sgm_18-2pts-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by the model based on the
	East Greenland margin. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:synt-margin-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 18$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:synt-margin-step1}.}
	\label{fig:synt-margin-step3-sgm18}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_X_1_2_1_2-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
	Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$, $\tilde{\mu}_{2} = 10^{2}$,
	$\tilde{\mu}_{3} = 10^{1}$ and $\tilde{\mu}_{4} = 10^{2}$.
	(Bottom panel) True and estimated surfaces,
	initial basement and Moho (initial guess) and a 
	priori information at points on basement and Moho (known depths).
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Gravity disturbance produced by the true 
	model (simulated data), estimated model (predicted data) and 
	by the initial guess (initial guess data). 
	The density contrasts are those shown in 
	Table~\ref{tab:simple-model} and $S_{0} = 40$ km.}
	\label{fig:simple-model-step1}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_2_1_2_1_2-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
	Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{2}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:simple-model-step1}.}
	\label{fig:simple-model-step2-u0-2}
}

\plot{E-model-rifted-margin-grafics-estimated-model-alphas_3_1_2_1_2-dpi300}{width=0.6\textwidth}{
	{Application to synthetic data produced by a simple model. 
		Estimated model $\mathbf{p}^{(2)}$ 
		obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
		using $\tilde{\mu}_{0} = 10^{3}$.
		The remaining information is the same shown in the caption of
		Figure~\ref{fig:simple-model-step1}.}
	\label{fig:simple-model-step2-u0-3}
}

@@

\plot{map-line-localization-test-dpi300}{width=0.8\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Gravity disturbance
	provided by the global gravity field model EIGEN-6C4 \citep{forste2014} at
	the study area. The black straight line indicates the gravity profile over the Pelotas
	basin. The end points of the profile have coordinates (geodetic latitude and longitude) 
	$(-27.72^{\circ}, -48.23^{\circ})$ and $(-29.66^{\circ}, -44.94^{\circ})$. 
	The coordinates are referred to the WGS84 datum.}
	\label{fig:pelotas-location}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_X_1_2_1_2-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(1)}$ 
	obtained at the end of Step 1 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{1} = 10^{1}$, $\tilde{\mu}_{2} = 10^{2}$,
	$\tilde{\mu}_{3} = 10^{1}$ and $\tilde{\mu}_{4} = 10^{2}$.
	(Bottom panel) Estimated surfaces, initial basement and Moho (initial guess) 
	and a priori information at basement and Moho (known depths).
	The continuous black lines represent a previous interpretation presented 
	by \citet{zalan2015}.
	(Middle panel) True and predicted lithostatic stress curves 
	(equation~\ref{eq:lithostatic-stress-matrix}).
	(Upper panel) Observed gravity disturbance, data produced by the estimated
	model (predicted data) and data produced the by the initial approximation (initial guess data).
	We used $S_{0} = 41$ km, density contrasts equal to those shown in Table~\ref{tab:pelotas-model}
	and initial approximation for $\Delta S$ equal to $1$ km.}
	\label{fig:pelotas-step1}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(2)}$ 
	obtained at the end of Step 2 (Figure~\ref{fig:flow-diagram}) by
	using $\tilde{\mu}_{0} = 10^{2}$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step2}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_7-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 7$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm7}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_17dot6-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 17.6$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm17dot6}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_19-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}) by
	using $\mathbf{p}^{(2)}$ (Figure~\ref{fig:pelotas-step2}) as
	initial approximation (dashed blue lines) and
	$\sigma = 19$ (equation~\ref{eq:elements-wii}).
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-sgm19}
}

\plot{pelotas-profile-grafics-estimated-model-alphas_2_1_2_1_2-sgm_17-T07-dpi300}{width=0.6\textwidth}{
	{Application to real data on Pelotas basin, Brazil. Alternative estimated model $\mathbf{p}^{(3)}$ 
	obtained at the end of Step 3 (Figure~\ref{fig:flow-diagram}). 
	The differences between this model and those shown in Figures \ref{fig:pelotas-step3-sgm7},
	\ref{fig:pelotas-step3-sgm17dot6} and \ref{fig:pelotas-step3-sgm19} are the
	densities $\rho^{(1)}$ and $\rho^{(2)}$ attributed to the sediments
	and SDR (Table~\ref{tab:pelotas-model}), as well as the parameter 
	$\sigma$ (equation~\ref{eq:elements-wii}).
	In this alternative model, $\rho^{(1)} = 2425$ kg/m$^{3}$,
	$\rho^{(2)} = 2835$ kg/m$^{3}$ and $\sigma = 17$.
	The remaining information is the same shown in the caption of
	Figure~\ref{fig:pelotas-step1}.}
	\label{fig:pelotas-step3-alternative}
}

@@

The authors are grateful to the editors E. Gasperikova, J. Shragge, X. Li, reviewers 
J. G. Abdeslem, Bob Ferderer and anonymous reviewers for their constructive comments 
and suggestions.
We are deeply indebted to the open-source Python toolkit for geophysical modeling and inversion
Fatiando a Terra \citep{uieda-etal2013}, the open-source libraries Numpy/Scipy 
\citep{jones_etal2001}
for array-based computations, matplotlib \citep{hunter2007} for plotting
and also Jupyter Notebook (\url{https://jupyter.org/}) for putting all together. 
V. C. Oliveira Jr was supported by fellowships from the brazilian research agencies 
CNPq (grant no. 308945/2017-4) and FAPERJ (grant no. E-26/202.729/2018).
